\begin{thebibliography}{1}
	
	\bibitem{bx-grace} K. Czarnecki, J. N. Foster, Z. Hu, R. L\"ammel, A. Sch\"urr, and J. F. Terwilliger,  {\em Bidirectional Transformations: A Cross-Discipline Perspective}, GRACE International Meeting , Shonan, Japan, 2008.
	
	\bibitem{bx-dagstuhl} Z. Hu, A. Sch\"urr, P. Stevens, and J. Terwilliger,  {\em Dagstuhl Seminar} \#11031 on Bidirectional Transformations "bx", Dagstuhl Reports, Vol. 1, Issue 1, pages 42-67, January 16-21 , 2011.
	
	\bibitem{bx-theoryandappl} J. Gibbons, R. F. Paige, A. Sch\"urr, J. F. Terwilliger and J. Weber, {\em Bi-directional transformations (bx) - Theory and Applications Across Disciplines}, [Online]. Available:  https://www.birs.ca/workshops/2013/13w5115/report13w5115.pdf.
	
	\bibitem{benchmark-BX} R. Oppermann and P. Robrecht, {\em Benchmarks for Bidirectional Transformations.} Seminar Maintaining Consistency in Model-Driven Engineering: Challenges and Techniques, University of Paderborn: Summer Term 2016.
	
	\bibitem{benchmarx} A. Anjorin, A. Cunha, H. Giese, F. Hermann, A. Rensink, and A. Sch\"urr, {\em Benchmarx}. In K. S. Candan, S. Amer-Yahia, N. Schweikardt, V. Christophides, and V. Leroy, editors, Proceedings of the Workshops of the EDBT/ICDT 2014 Joint Conference (EDBT/ICDT 2014), CEUR Workshop Proceedings, pages 82-86. CEUR-WS.org, 2014.
		
	\bibitem{benchmarx-reload} A. Anjorin, Z. Diskin, F. Jouault, Hsiang-Shang Ko, E. Leblebici, and B. Westfechtel, {\em Benchmarx Reloaded: A Practical Benchmark Framework for Bidirectional Transformations}. In R. Eramo, M. Johnson (eds.): Proceedings of the Sixth International Workshop on Bidirectional Transformations (Bx 2017),
	Uppsala, Sweden, April 29, 2017, published at http://ceur-ws.org.
	
	\bibitem{tgg} A. Sch\"urr. {\em Specification of graph translators with triple graph grammars.} In E. W. Mayr, G. Schmidt, and G. Tinhofer, editors, {\em Graph-Theoretic
	Concepts in Computer Science, 20th International Workshop, WG 94}, volume 903 of LNCS, pages 151-163, Herrsching, Germany, June 1994.
	
	\bibitem{bx-tgg} A. Bucaioni and R. Eramo, {\em Understanding bidirectional transformations with TGGs and JTL}, in Proc. of the Second Workshop on Bidirectional Transformations (BX 2013), no. 57, 2013.
	
	\bibitem{emoflon-part4} A. Anjorin, E. Burdon, F. Deckwerth, R. Kluge, L. Kliegel, M. Lauder, E. Leblebici, D.T\"ogel, D. Marx, L. Patzina, S. Patzina, A. Schleich, S. E. Zander, J. Reinl\"ander, and M. Wieber, {\em An Introduction to	Metamodelling and Graph Transformations with eMoflon. Part IV: Triple Graph Grammars.} [Online]. Available: 
	https://emoflon.github.io/eclipse-plugin/release/handbook/part4.pdf
	
	\bibitem{bx-community} BX Community, [Online]. Available: http://bx-community.wikidot.com/
	
	\bibitem{bx-examples} BX Community, [Online]. Available: http://bx-community.wikidot.com/examples:home
	
	\bibitem{echo} N. Macedo, T. Guimar\"aes and A. Cunha, {\em Model repair and transformation with Echo}. In Proc. ASE 2013, ACM Press, 2013.
	
	\bibitem{bigul} Hsiang-Shang Ko, Tao Zan, and Zhenjiang Hu, {\em BiGUL: A formally verified core language for putback-based bidirectional programming.} In Partial Evaluation and Program Manipulation, PEPM'16, pages 61-72, ACM, 2016.
	
	\bibitem{bigul-tutorial} Zhenjiang Hu and Hsiang-Shang Ko,  {\em Principle and Practice of Bidirectional Programming in BiGUL}, Tutorial [Online]. Available: http://www.prg.nii.ac.jp/project/bigul/tutorial.pdf
	
	\bibitem{biyacc} {\em BiYacc, tool designed to ease the work of writing parsers and printers}, [Online]. Available: http://biyacc.yozora.moe/
	
	\bibitem{share} {\em SHARE - Sharing Hosted Autonomous Research Environments}, [Online]. Available: http://is.ieis.tue.nl/staff/pvgorp/share/
	
	\bibitem{wiki-transformation} {\em Wikipedia. "Model transformation."} Retrieved March, 2017, from https://en.wikipedia.org/wiki/Model{\_}transformation.
	
	\bibitem{semethods} S. Easterbrook, J. Singer, M.-A. Storey, \& D. Damian. {\em Selecting Empirical Methods for Software Engineering Research. Guide to Advanced Empirical Software Engineering}, 285-311, 2008. Retrieved from http://doi.org/10.1007/978-1-84800-044-5\_11
	
	\bibitem{uml} J. Rumbaugh, I. Jacobson and G. Booch, {\em Unified Modeling Language Reference Manual, The (2nd Edition)}, Pearson Higher Education, pages 1-21, 2004.
	
	\bibitem{mdsd} S. Beydeda, M. Book and V. Gruhn, {\em Model-Driven Software Development}, ACM Computing Classification, pages 1-8, 1998.
	
	\bibitem{modeltransform} S. Sendall and W. Kozaczynski, {\em Model transformation: the heart and soul of model-driven software development},  IEEE, Vol. 20, Issue: 5, pages 42-45, Sept.-Oct. 2003.
	
	
\end{thebibliography}



