\begin{thebibliography}{1}
	
	\bibitem{bx-grace} K. Czarnecki, J. N. Foster, Z. Hu, R. L\"ammel, A. Sch\"urr, and J. F. Terwilliger,  {\em Bidirectional Transformations: A Cross-Discipline Perspective}, GRACE International Meeting , Shonan, Japan, 2008.
	
	\bibitem{bx-dagstuhl} Z. Hu, A. Sch\"urr, P. Stevens, and J. Terwilliger, {\em Dagstuhl Seminar \#11031 on Bidirectional Transformations "bx"}, Dagstuhl Reports, vol. 1, Issue 1, pages 42-67, January 16-21, 2011.
	
	\bibitem{bx-theoryandappl} J. Gibbons, R. F. Paige, A. Sch\"urr, J. F. Terwilliger and J. Weber, {\em Bi-directional transformations (bx) - Theory and Applications Across Disciplines}, [Online]. Available:  https://www.birs.ca/workshops/2013/13w5115/report13w5115.pdf.
	
	\bibitem{benchmark-BX} R. Oppermann and P. Robrecht, {\em Benchmarks for Bidirectional Transformations}, Seminar Maintaining Consistency in Model-Driven Engineering: Challenges and Techniques, University of Paderborn: Summer Term 2016.
	
	\bibitem{benchmarx} A. Anjorin, A. Cunha, H. Giese, F. Hermann, A. Rensink, and A. Sch\"urr, {\em Benchmarx}, In K. S. Candan, S. Amer-Yahia, N. Schweikardt, V. Christophides, and V. Leroy, (eds.). In Proc. of the Workshops of the EDBT/ICDT 2014 Joint Conference (EDBT/ICDT 2014), CEUR Workshop Proceedings, pages 82-86, 2014.
		
	\bibitem{benchmarx-reload} A. Anjorin, Z. Diskin, F. Jouault, Hsiang-Shang Ko, E. Leblebici, and B. Westfechtel, {\em Benchmarx Reloaded: A Practical Benchmark Framework for Bidirectional Transformations}, In R. Eramo, M. Johnson (eds.). In Proc. of the Sixth International Workshop on Bidirectional Transformations (Bx 2017),
	Uppsala, Sweden, April 29, 2017, published at http://ceur-ws.org.
	
	\bibitem{tgg} A. Sch\"urr. {\em Specification of graph translators with triple graph grammars}, In E. W. Mayr, G. Schmidt, and G. Tinhofer (eds.). In Proc. of the 20th International Workshop, Graph-Theoretic Concepts in Computer Science, WG 94, vol. 903, pages 151-163, Herrsching, Germany, June 1994.
	
	\bibitem{bx-tgg} A. Bucaioni and R. Eramo, {\em Understanding bidirectional transformations with TGGs and JTL}, In Proc. of the Second Workshop on Bidirectional Transformations (BX 2013), vol. 57, 2013.
	
	\bibitem{emoflon-part4} A. Anjorin, E. Burdon, F. Deckwerth, R. Kluge, L. Kliegel, M. Lauder, E. Leblebici, D.T\"ogel, D. Marx, L. Patzina, S. Patzina, A. Schleich, S. E. Zander, J. Reinl\"ander, and M. Wieber, {\em An Introduction to Metamodelling and Graph Transformations with eMoflon. Part IV: Triple Graph Grammars}, [Online]. Available: 
	https://emoflon.github.io/eclipse-plugin/release/handbook/part4.pdf
	
	\bibitem{bx-community} {\em BX Community}, [Online]. Available: http://bx-community.wikidot.com/
	
	\bibitem{bx-examples} {\em BX Examples}, [Online]. Available: http://bx-community.wikidot.com/examples:home
	
	\bibitem{echo} N. Macedo, T. Guimar\"aes and A. Cunha, {\em Model repair and transformation with Echo}, In Proc. of ASE 2013, ACM Press, 2013.
	
	\bibitem{bigul} Hsiang-Shang Ko, Tao Zan, and Zhenjiang Hu, {\em BiGUL: A formally verified core language for putback-based bidirectional programming}, In Proc. of Partial Evaluation and Program Manipulation, pages 61-72, ACM, 2016.
	
	\bibitem{bigul-tutorial} Z. Hu and H.-Shang Ko,  {\em Principle and Practice of Bidirectional Programming in BiGUL}, Tutorial [Online]. Available: http://www.prg.nii.ac.jp/project/bigul/tutorial.pdf
	
	\bibitem{biyacc} {\em BiYacc, tool designed to ease the work of writing parsers and printers}, [Online]. Available: http://biyacc.yozora.moe/
	
	\bibitem{share} {\em SHARE - Sharing Hosted Autonomous Research Environments}, [Online]. Available: http://is.ieis.tue.nl/staff/pvgorp/share/
	
	\bibitem{virtualbox} {\em VM Virtual Box}, [Online]. Available: https://www.virtualbox.org/
	
	\bibitem{google-forms} {\em Google Forms}, [Online]. Available: https://www.google.com/forms/about/
	
	\bibitem{understanding-bx} A. Bucaioni and R. Eramo, {\em Understanding bidirectional transformations with TGGs and JTL}, In Proc. of the Second International Workshop on BX, 2013.
	
	\bibitem{modelsynchro-tgg} F. Hermann et al., {\em Model synchronization based on triple graph grammars: correctness, completeness and invertibility}, Software and Systems Modeling, vol. 14, pages 241-269, 2013.
	
	\bibitem{semethods} S. Easterbrook, J. Singer, M.-A. Storey, \& D. Damian. {\em Selecting Empirical Methods for Software Engineering Research. Guide to Advanced Empirical Software Engineering}, pages 285-311, 2008. Retrieved from http://doi.org/10.1007/978-1-84800-044-5\_11
	
	\bibitem{uml} J. Rumbaugh, I. Jacobson and G. Booch, {\em Unified Modeling Language Reference Manual, The (2nd Edition)}, Pearson Higher Education, pages 1-21, 2004.
	
	\bibitem{mdsd} S. Beydeda, M. Book and V. Gruhn, {\em Model-Driven Software Development}, ACM Computing Classification, pages 1-8, 1998.
	
	\bibitem{modeltransform} S. Sendall and W. Kozaczynski, {\em Model transformation: the heart and soul of model-driven software development},  IEEE, vol. 20, Issue: 5, pages 42-45, Sept.-Oct. 2003.
	
	\bibitem{designpattern} E. Gamma, R. Helm, R. Johnson and J. Vlissides, {\em Design Patterns}, Addison-Wesley, vol. 47, Boston Massachusetts USA, 1995.
	
	\bibitem{designpattern-notes} E. Gamma, R. Helm, R. Johnson and J. Vlissides, {\em Design Patterns: Abstraction and Reuse of Object-Oriented Design}, In O.M. Nierstrasz (eds.). ECOOP 1993 - Object-Oriented Programming, Lecture Notes in Computer Science, Springer, vol. 707, Berlin, Heidelberg.
	
	\bibitem{mvc-arch} J. Deacon, { \em Model-view-controller (mvc) architecture}, Computer Systems Development, pages 1-6, 2009.
	
	\bibitem{mdd-webwithmvc} D. Distante, P. Pedone, G. Rossi and G. Canfora, { \em Model-driven development of Web applications with UWA, MVC and JavaServer faces}, Lecture Notes in Computer Science (including subseries Lecture Notes in Artificial Intelligence and Lecture Notes in Bioinformatics), vol. 4607, pages 457-472, 2007.
	
	\bibitem{designpattern-headfirst} E. Freeman, E. Robson, K. Sierra and B. Bates, { \em Head First Design Patterns}, O'Reilly, pages 536-566, USA, 2004.
	
	\bibitem{canvas} {\em MDN, "Canvas API",} Retrieved May, 2017, from https://developer.mozilla.org/en-US/docs/Web/API/Canvas\_API.
	
	\bibitem{fabricjs} {\em Fabric.js}, [Online]. Available: http://fabricjs.com/.
	
	\bibitem{processingjs} {\em Processing.js}, [Online]. Available: http://processingjs.org/.
	
	\bibitem{pixijs} {\em Pixi.js}, [Online]. Available: http://www.pixijs.com/.
	
	\bibitem{javascript} D. Goodman and M. Morrison, {\em Javascript Bible}, Wiley Publishing Inc., 6th Edition, pages 1-8, Indianapolis, Indiana, 2007.
	
	\bibitem{designinterfaces} J. Tidwell, {\em Designing interfaces}, O'Reilly, vol. XXXIII, Pages 81-87, 2012.
	
	\bibitem{scenariobasedui} K. Kusano, M. Nakatani and T. Ohno, {\em Scenario-based interactive UI design}, In Proc. of the SIGCHI Conference on Human Factors in Computing Systems - CHI '13, 2013.
	
	\bibitem{servlet} J. Hunter and W. Crawford, {\em Java servlet programming}, vol. 37, 2001.
	
	\bibitem{funcandnonfuncreq} P. Sharma and S. Dhir, {\em Functional \& non-functional requirement elicitation and risk assessment for agile processes}. International Journal of Control Theory and Applications, vol. 9, pages 9005-9010, 2016.
	
	\bibitem{analysisprepostdesigns} P.L. Bonate, {\em Analysis of pretest posttest designs}, FL: Chapman \& Hall/CRC, pages 1-5, 2000.
	
	\bibitem{expandquasiexpdesign} D.T. Campbell \& J.C. Stanley, {\em Experimental and quasi-experimental designs for research }, In N. L. Gage (eds.), Handbook of research on teaching, Rand McNally, Chicago, 1963.
	
	\bibitem{anovapreposttest} S.W. Huck \& R.A. McLean, {\em Using a Repeated Measures ANOVA to Analyze the Data from a Pretest-Posttest Design: A Potentially Confusing Task }, Psychological Bulletin, vol. 82, No. 4, pages 511-518, 1975. 
	
	\bibitem{validitythreatsinse} R. Feldt \& A. Magazinius, {\em Validity Threats in Empirical Software Engineering Research - An Initial Survey } , In Proc. of the International Conference on Software Engineering and Knowledge Engineering, issue March, pages 374-379, 2010.
	
	\bibitem{expinse} C. Wohlin, M. H\"ost, P. Runeson, M. Ohlsson, B. Regnell, and A. Wesslen, {\em Experimentation in software engineering: an introduction }, Kluwer Academic Publishers, 2000.
	
	
\end{thebibliography}



